Automated Topic Naming

### 2012-01-20 ese/ese.tex
black and white compatible

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/postgresql-author-cluster}
  \caption{PostgreSQL Author Clusters: Authors clustered by Euclidean
    distance of their NFR contributions. The outer rectangles (blue)
    reflect the clustering of authors into 2 clusters; while the inner rectangles
    (purple) reflect clustering of authors into 6 clusters. The height is a
    measure of cluster similarity, Euclidean distance, where smaller
    values are more similar. Individuals that share
    branches are more similar to each other individuals who do
    not. The longer the path, in terms of height, between two
    individuals, the more different their NFR contributions are.}
\label{fig:authorcluster}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/postgresql-author-cluster}
  \caption{PostgreSQL Author Clusters: Authors clustered by Euclidean
    distance of their NFR contributions. The outer rectangles (black)
    reflect the clustering of authors into 2 clusters; while the inner rectangles
    (dim grey) reflect clustering of authors into 6 clusters. The height is a
    measure of cluster similarity, Euclidean distance, where smaller
    values are more similar. Individuals that share
    branches are more similar to each other individuals who do
    not. The longer the path, in terms of height, between two
    individuals, the more different their NFR contributions are.}
\label{fig:authorcluster}
\end{figure}
